---
title: "Ice bath trails"
output: html_notebook
---

```{r, echo=F, message=F }
rm(list = ls())
Code='e:/Fellowship/UoB-MarineScotland/Code/'

Ice26=read.csv(paste0(Code,'Icebath-26jan.csv'),stringsAsFactors =  F)
Ice26$d <-as.POSIXlt(Ice26$Time, format = '%d/%m/%Y %H:%M')
Ice27=read.csv(paste0(Code,'Icebath_27-28Dec.csv'),stringsAsFactors =  F)
Ice27$d <-as.POSIXlt(Ice27$Time, format = '%d/%m/%Y %H:%M:%S')


```

### Icebath experiment
From 12:19 27th January until 9:10 28 January
Sensors are in small plastic tupperware with ice cubes from 12:19 until the next morning.

```{r, echo=FALSE}
plot(Ice27$d,Ice27$DigitalTherm, col='orange', xlab='Time from 12:19 27th Jan to 9:10 28th Jan', ylab='Temperature (degrees Celcius)')
points(Ice27$d,Ice27$Thermistor,col='blue')
points(Ice27$d,Ice27$DigitalTherm,col='orange')
legend('topleft',c('Digital thermometer','Thermistor'), col=c('orange','blue'),pch=1)
```
> Zoom in to a range of -.5 to 1 degree Celcius  
Cooling of thermometers (mean in plot)

Data selected from -0.1 - 1 degree Celcius

```{r, echo=FALSE,warning=FALSE}
#select( Times) # more or less 0-warming up
library(dplyr)

Tmistor01= Ice27 %>% filter(Thermistor>= -0.1 & Thermistor <=1)
Tdigital01=Ice27 %>% filter(DigitalTherm>= -.1 & DigitalTherm <=1)
#summary(Tmistor01$Thermistor)
#summary(Tdigital01$DigitalTherm)

{
plot(Tdigital01$d,Tdigital01$DigitalTherm, col='orange', xlab='Time from 12:19 to 16:45 on 27th Jan', ylab='Temperature (degrees Celcius)', ylim=c(-0.1,1.1))
points(Tmistor01$d,Tmistor01$Thermistor,col='blue')
# lines(Tmistor01$d,Tmistor01$Thermistor,col='blue')
legend('topright',c('Digital Thermometer','Thermistor'), col=c('orange','blue'),pch=1)
text(y=1.1,x=as.POSIXlt('2021-01-27 13:10:00 GMT'),paste('Mean temp. digital thermometer',round(mean(Tdigital01$DigitalTherm),3)))
text(y=1,x=as.POSIXlt('2021-01-27 13:10:00 GMT'),paste('Mean temp. thermistor',round(mean(Tmistor01$Thermistor),3)))

}

#> look for dT 
# Tmistor01$diff<- c(0,diff(Tmistor01$Thermistor, lag=1))
# min(Tmistor01$diff)
# max(Tmistor01$diff)
# summary(Tmistor01$diff)
```
> Stabilisation period
Last hours of trail when water temperature is stable.
From 20:16 27th Jan to 9:10 28th Jan

Data selection from 13.5 - 15.5 degrees Celcius

-note that heating went on at 7:00.!

```{r, echo=FALSE}

Tmistor1415= Ice27 %>% filter(Thermistor>= 13.5 & Thermistor <=15.5)
Tdigital1415=Ice27 %>% filter(DigitalTherm>= 13.5 & DigitalTherm <=15.5)
# summary(Tmistor1415$Thermistor)
# summary(Tdigital1415$DigitalTherm)
#diff
Tmistor1415$diff<- c(0,diff(Tmistor1415$Thermistor, lag=1))
# min(Tmistor1415$diff)
# max(Tmistor1415$diff)
# summary(Tmistor1415$diff)
print('Absolute step changes thermistor')
unique(abs(Tmistor1415$diff)) # step changes (absolute difference between measurements)

Tdigital1415$diff<- c(0,diff(Tdigital1415$DigitalTherm, lag=1))
# min(abs(Tdigital1415$diff))
# max(Tdigital1415$diff)
# summary(Tdigital1415$diff)
print('Absolute step changes Digital thermometer')
unique(abs(Tdigital1415$diff)) #step change (absolute difference between measurements)

{
plot(Tdigital1415$d,Tdigital1415$DigitalTherm, col='orange', xlab='Time from 20:16 27th Jan to 9:10 28th Jan', ylab='Temperature (degrees Celcius)', ylim=c(13.3,15.5),cex=0.5)
points(Tmistor1415$d,Tmistor1415$Thermistor,col='blue')
# lines(Tmistor01$d,Tmistor01$Thermistor,col='blue')
legend('topright',c('Digital Thermometer','Thermistor'), col=c('orange','blue'),pch=1)
text(y=15.2,x=as.POSIXlt('2021-01-27 23:30:00 GMT'),paste('Step change thermistor 0.02'))
text(y=15.4,x=as.POSIXlt('2021-01-27 23:30:00 GMT'),paste('Step change d.thermometer 0.06'))

}


```

Mean values are 14.35 (digital thermometer) and 14.26 (thermistor)
-- step change is most interesting (shown in plot)

### Follow up:
> compare the two thermistors and digital signal

or

> compare to tiny tag - compare to reference - calibrated.
when other thermistor

### Accuracy analogue to digital convertion [in lab]
> 8bit to 1023 values


### Calibrating the sensor [in lab]
> range of values -15 -  30

